Textmining in Economics

### 2017-10-31 paper/R/01_prepare.Rmd
fancy graphs

## Clean Data
```{r}
df %>%
  mutate(fb_shares = as.numeric(fb_shares),
         fb_likes = as.numeric(fb_likes),
         fb_comments = as.numeric(fb_comments)) -> df
```

@@

## Count number of terms in a string
```{r}
df %>% filter(site != "zdf.de") -> df

df$text_lenght <- sapply(gregexpr("\\S+", df$text), length)
```

>>>>

## Clean Data
```{r}
df %>%
  mutate(fb_shares = as.integer(fb_shares),
         fb_likes = as.integer(fb_likes),
         fb_comments = as.integer(fb_comments)) -> df
```

@@

## Count number of terms in a string
```{r}
df$text_length <- sapply(gregexpr("\\S+", df$text), length)
```

### 2017-10-31 paper/R/01_prepare_eventbride.Rmd
fancy graphs

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)

```

@@

load("../output/news_cleaned.Rda")
```

@@

```{r}
df %>%
  distinct(text, .keep_all = TRUE) -> df
```

```{r}
pat <- 'Aus unserem Netzwerk[^"]*'
btw %>%
  filter(grepl(pat, text, perl = TRUE)) %>%
  group_by(site) %>%
  tally(sort = TRUE)
```
```{r}
as.data.frame(str_match(btw$text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1]
```

@@

```{r}
# Save file
save(df, file="../output/news_cleaned2.Rda")
```

@@

```{r}
save(df, file="../output/news_cleaned2.Rda")
```

## Generate new variables 
```{r}
df$video <- ifelse(grepl("video", df$title, ignore.case = TRUE),1,0)
df$date <- as.Date(df$date)
```

## Reduce Dataframe
```{r}
df %>%
  filter(!site %in% c("ndr.de","wdr.de", "swr.de","tagessschau.de")) %>%
  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw

btw$ArticleID <- rownames(btw)
```

```{r}
save(df, btw, file="../output/news_btw.Rda")
```

>>>>

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

@@

df <- read_csv("../data/eventbride/eventbride_okt_18.csv")
```

# Generate new variables 
```{r}
## Extract site
df$site <- str_extract(df$source, "(?<='uri': ')[A-z][^']*")

# Is video
df$video <- ifelse(grepl("video", df$title, ignore.case = TRUE),1,0)

# number of Facebook shares
df$fb_shares <- str_extract(df$shares, "(?<='facebook': )[0-9]*")
df$fb_shares <- ifelse(is.na(df$fb_shares),0, df$fb_shares)
df$fb_shares <- as.integer(df$fb_shares)

# Text Length
names(df) <- gsub("body", "text", names(df))
df$text_length <- sapply(gregexpr("\\S+", df$text), length)
```

```{r}
ggplot(df, aes(site, fill=as.factor(isDuplicate))) +
  geom_bar(alpha=.6) +
  labs(x="", y="", fill="is Duplicate") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

```{r}
# Save file
save(df, file="../output/news_cleaned_eventbride.Rda")
```

```{r}
pat <- 'ejf[^"]*'
df %>%
  filter(grepl(pat, text, perl = TRUE)) %>%
  group_by(site) %>%
  tally(sort = TRUE)
```

```{r}
as.data.frame(str_match(df$text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1]
```

@@

@@

```{r}
# Save file
save(df, file="../output/news_cleaned_eventbride.Rda")
```

@@

```{r}
df -> df2
```

```{r}
save(df2, file="../output/news_cleaned_eventbride.Rda")
```

## Reduce Dataframe
```{r}
keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )

df2 %>%
  filter(isDuplicate == "False") %>%
  filter(site %in% keeps) %>%
  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw2
```

```{r}
save(df2, btw2, file="../output/news_btw2.Rda")
```

### 2017-10-31 paper/R/02_combine.Rmd
fancy graphs

# Load and prepare Dataframe

```{r}
rm(list =ls())

load("../output/news_cleaned.Rda")
```

@@

```{r}
df %>%
  distinct(text, .keep_all = TRUE) -> df
```

```{r}
pat <- 'Aus unserem Netzwerk[^"]*'
btw %>%
  filter(grepl(pat, text, perl = TRUE)) %>%
  group_by(site) %>%
  tally(sort = TRUE)
```
```{r}
as.data.frame(str_match(btw$text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1]
```

@@

# apply function to dataframe
df$text_cleaned <- clean.text(df$text)
```

```{r}
df$text_cleaned <- gsub("[[:punct:]]", " ", df$text_cleaned)
df$text_cleaned <- gsub("[[:cntrl:]]", " ", df$text_cleaned)
df$text_cleaned <- gsub("[[:digit:]]", " ", df$text_cleaned)
df$text_cleaned <- gsub("^[[:space:]]+", " ", df$text_cleaned)
df$text_cleaned <- gsub("[[:space:]]+$", " ", df$text_cleaned)
df$text_cleaned <- tolower(df$text_cleaned)
```

```{r}
# Save file
save(df, file="../output/news_cleaned2.Rda")
```

## Remove Stopwords
```{r}
df$text_cleaned<- removeWords(df$text_cleaned, stopwords("german"))
```

@@

df$text_cleaned<- removeWords(df$text_cleaned, mystopwords$mystopwords)
```

```{r}
save(df, file="../output/news_cleaned2.Rda")
```

## Generate new variables 
```{r}
df$video <- ifelse(grepl("video", df$title, ignore.case = TRUE),1,0)
df$date <- as.Date(df$date)
```

## Reduce Dataframe
```{r}
df %>%
  filter(!site %in% c("ndr.de","wdr.de", "swr.de","tagessschau.de")) %>%
  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw

btw$ArticleID <- rownames(btw)
```

```{r}
save(df, btw, file="../output/news_btw.Rda")
```

>>>>

# Load and prepare Dataframes
```{r}
rm(list =ls())

load("../output/news_cleaned.Rda")
df2 <- read_csv("../data/eventbride/eventbride_okt_18.csv")
```

## Generate new variables 
```{r}
## Extract site
df2$site <- str_extract(df2$source, "(?<='uri': ')[A-z][^']*")

# number of Facebook shares
df2$fb_shares <- str_extract(df2$shares, "(?<='facebook': )[0-9]*")
df2$fb_shares <- ifelse(is.na(df2$fb_shares),0, df2$fb_shares)
df2$fb_shares <- as.integer(df2$fb_shares)

# Text Length
names(df2) <- gsub("body", "text", names(df2))
df2$text_length <- sapply(gregexpr("\\S+", df2$text), length)
```

## Reduce Dataframe
```{r}
keeps <- c( "welt.de","spiegel.de","stern.de","focus.de","zeit.de","bild.de" )

df %>%
  filter(site %in% keeps) %>%
  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw1

df2 %>%
  filter(site %in% keeps) %>%
  filter(grepl("bundestagswahl", text, ignore.case = TRUE)) -> btw2
```

## Combine Dataframes
```{r}
common_cols <- intersect(colnames(btw1), colnames(btw2))

btw <- rbind(
  btw1[, common_cols], 
  btw2[, common_cols]
)
```

```{r}
btw$title.text <- paste(btw$title, btw$text, sep = " ")
```

@@

## Filtering
```{r}
btw %>%
  # Keep unique observations
  distinct(title, site, .keep_all = TRUE) %>%
  # Remove Articles after 10.10.2017
  filter(date < as.Date("2017-10-10")) -> btw
```

```{r}
pat <- 'Aus unserem Netzwerk[^"]*'
btw %>%
  filter(grepl(pat, text, perl = TRUE)) %>%
  group_by(site) %>%
  tally(sort = TRUE)
```

```{r}
as.data.frame(str_match(btw$text, pat)) ->test
test %>%
  filter(!is.na(test)) %>%
  .[1]
```

@@

# apply function to dataframe
btw$text_cleaned <- clean.text(btw$title.text)
```

```{r}
btw$text_cleaned <- gsub("[[:punct:]]", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("[[:cntrl:]]", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("[[:digit:]]", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("^[[:space:]]+", " ", btw$text_cleaned)
btw$text_cleaned <- gsub("[[:space:]]+$", " ", btw$text_cleaned)
btw$text_cleaned <- tolower(btw$text_cleaned)
```

## Remove Stopwords
```{r}
btw$text_cleaned<- removeWords(btw$text_cleaned, stopwords("german"))
```

@@

btw$text_cleaned<- removeWords(btw$text_cleaned, mystopwords$mystopwords)
```

## Stemming
```{r}
stem_text<- function(text, language = "porter", mc.cores = 1) {
  # stem each word in a block of text
  stem_string <- function(str, language) {
    str <- strsplit(x = str, split = "\\s")
    str <- wordStem(unlist(str), language = language)
    str <- paste(str, collapse = " ")
    return(str)
  }

  # stem each text block in turn
  x <- mclapply(X = text, FUN = stem_string, language, mc.cores = mc.cores)

  # return stemed text blocks
  return(unlist(x))
}

btw$text_cleaned <- stem_text(btw$text_cleaned)
```

```{r}
save(btw, file="../output/btw_combined.Rda")
```

### 2017-10-31 paper/R/04_paper.Rmd
fancy graphs

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","topicmodels",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

@@

load("../output/news_btw.Rda")

df$date <- as.Date(df$date)
```

```{r, include=FALSE}
df %>%
  #filter(fb_shares > 0) %>%
  filter(!site %in% c("ndr.de","wdr.de","swr.de","tagesschau.de")) %>%
  filter(grepl("bundestagswahl", text_cleaned)) -> btw

btw 
```

To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 1768 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 30.09.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from seven different german news sources.\footnote{Bild.de, Focus.de, Handelsblatt.com, Spiegel.de, Stern.de, Tagesschau.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the report. We include the news agency as covariates on topical prevalence. We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies.

Figure -- shows the total sum of all Facebook S, that most of the documents in our corpus

```{r echo=FALSE}
btw %>%
  filter(!grepl("video", title, ignore.case = TRUE)) %>%
  ggplot(aes(x=as.factor(site), y=fb_shares)) +
  stat_summary(fun.y="sum", geom="bar", fill = "blue", alpha = .5) +
  labs(title = "") +
  labs(x="", y="Sum of Facebook Shares") +
  theme(axis.text.x = element_text(angle = 40, hjust = 1))
```

>>>>

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","topicmodels",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","ggthemes","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

@@

load("../output/btw_combined.Rda")
```

To explore the effect of topic prevalence of an article on the times this article is shared on Facebook, we analyze a sample of 6578 news articles containing the term "Bundestagswahl" (Federal Election) dated from 01.06.2017 to 10.10.2017\footnote{German federal elections took place on 24th of September 2017.} and originated from seven different german news sources.\footnote{Bild.de, Focus.de, Spiegel.de, Stern.de, Welt.de, Zeit.de} For each document in our sample, we observe the day it was written, the number of shares on Facebook and the newswire service publishing the report. We include the month the document was writte and the news agency as covariates on topical prevalence. We also include news agency as a covariate affecting topical content to estimate how topics are discussed in different ways by different news agencies \citep{roberts_model_2016}.
To determine the number of topics, we use a cross-validation scheme and maximize topics' coherence while changing the number of topics \citep{airoldi_reconceptualizing_2010}.

Figure -- shows the number of articles by news agency and the how many of these articles were shared on Facebook.

```{r echo=FALSE}
btw$shared <- ifelse(btw$fb_shares == 0, "0", NA)
btw$shared <- ifelse(btw$fb_shares > 0 | btw$fb_shares >= 100, "0-100", btw$shared)
btw$shared <- ifelse(btw$fb_shares > 100, "> 100", btw$shared)

btw %>%
  ggplot(aes(site, fill=shared)) +
  geom_bar(alpha = .9) +
  labs(x="", y="Count") +
  scale_fill_ptol("Shared on\n Facebook") +
  theme_minimal()
```

```{r}
btw %>%
  filter(site=="zeit.de") %>%
  select(title) %>%
  .[2,]
```

### 2017-10-31 paper/R/06_explore_LDA.Rmd
fancy graphs

load(file ="../output/models/LDAGibbs 50 .Rda")
```

@@

doctopics.df %>%
  transmute(ArticleID = rownames(.),
            Topic1 = V1,
            Topic2 = V2,
            Topic3 = V3) -> doctopics.df

doctopics.df$ArticleID <- as.integer(doctopics.df$ArticleID)

# Add Topic to origian DF
btw <- btw %>%
  mutate(ArticleID = as.integer(ArticleID)) %>%
  inner_join(.,doctopics.df, by="ArticleID")
```

@@

### Create Topic Labels
```{r}
topicTerms <- btw.terms %>% gather(Topic)
topicTerms <- cbind(topicTerms, Rank = rep(1:30))
topicTerms <- topicTerms %>% filter(Rank < 5)

topicTerms <- topicTerms %>% mutate(Topic = stringr::word(Topic, 2))
topicTerms$Topic <- as.numeric(topicTerms$Topic)

topicLabel <- data.frame()
for (i in 1:50){
  z <- dplyr::filter(topicTerms, Topic==i)
  l <- as.data.frame(paste(z[1,2], z[2,2], z[3,2], z[4,2], sep = " "), stringAsFactors = FALSE)
  topicLabel <- rbind(topicLabel, l)
}
colnames(topicLabel) <- c("Label")

topicLabel
```

### Working with Theta (Topic prevalence)
```{r}
theta <- as.data.frame(posterior(ldaOut)$topics)
head(theta)
```

>>>>

load(file ="../output/models/LDAGibbs 40 .Rda")
```

@@

doctopics.df %>%
  transmute(title = rownames(.),
            topic1 = V1,
            Topic2 = V2,
            Topic3 = V3) -> doctopics.df

doctopics.df$ArticleID <- as.integer(rownames(doctopics.df))

# Add Topic to origian DF
btw1 <- btw %>%
  mutate(ArticleID = as.integer(ArticleID)) %>%
  inner_join(.,doctopics.df, by="ArticleID")
```

@@

### Create Topic Labels
```{r}
## Return the top 30 terms.
btw.terms <- as.data.frame(terms(ldaOut, 30), stringAsFactors = FALSE)

topicTerms <- btw.terms %>% gather(Topic)
topicTerms <- cbind(topicTerms, Rank = rep(1:30))
topicTerms <- topicTerms %>% filter(Rank < 5)

topicTerms <- topicTerms %>% mutate(topic = stringr::word(Topic, 2))
topicTerms$topic <- as.numeric(topicTerms$topic)

topicLabel <- data.frame()
for (i in 1:40){
  z <- dplyr::filter(topicTerms, topic==i)
  l <- as.data.frame(paste(z[1,2], z[2,2], z[3,2], z[4,2], sep = " "), stringAsFactors = FALSE)
  topicLabel <- rbind(topicLabel, l)
}
colnames(topicLabel) <- c("Label")
topicLabel$topic <- rownames(topicLabel)
```

### Working with Theta (Topic prevalence)
```{r}
theta <- as.data.frame(posterior(ldaOut)$topics)
gamma <- as.data.frame(posterior(ldaOut)$terms)
```

### 2017-10-31 paper/R/07_stm.Rmd
fancy graphs

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","topicmodels",
          "plyr","dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

@@

load("../output/news_cleaned2.Rda")

df$date <- as.Date(df$date)

#col <- brewer.pal(12, name = "Paired")
```

## Reduce Dataframe
```{r}
df %>%
  filter(fb_shares > 0) %>%
  filter(!site %in% c("ndr.de","wdr.de")) %>%
  filter(grepl("bundestagswahl", text_cleaned)) -> btw

btw$ArticleID <- rownames(btw)
```

@@

```{r, eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("date","site","text_cleaned","text")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

### Run the Model 
```{r}
k = 50 # Topics

t1 <- Sys.time()
stmOut <- stm(documents = out$documents, 
           vocab = out$vocab, 
           K=k, 
           prevalence = ~site, 
           content = ~site, 
           data=out$meta, 
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

>>>>

```{r, include=FALSE}
# load the packages
libs <- c("tidytext","tidyr","readr","lubridate","tm","stm","RColorBrewer","topicmodels",
          "dplyr","class","knitr","kableExtra","cldr","data.table",
          "htmlTable","ggplot2","gridExtra","jsonlite","stringr","scales","rjson")
lapply(libs, library, character.only = TRUE)
```

@@

load("../output/btw_combined.Rda")
```

```{r}
btw$month <- month(btw$date)
```

@@

```{r, eval=FALSE, include=FALSE}
# Process data
processed <- textProcessor(btw$text_cleaned, metadata = btw[,c("date","month","site","text_cleaned","text")],
                           wordLengths = c(2,Inf),
                           lowercase = F,
                           removestopwords = F,
                           removenumbers = F,
                           removepunctuation = F,
                           stem = F)
out <- prepDocuments(processed$documents, processed$vocab, processed$meta)
```

### Run the Model 
```{r}
k = 40 # Topics

t1 <- Sys.time()
stmOut <- stm(documents = out$documents, 
           vocab = out$vocab, 
           K=k, 
           prevalence = ~site+s(month), 
           content = ~site, 
           data=out$meta, 
           init.type = "Spectral")
t2 <- Sys.time()
t2 - t1

### 2017-10-31 paper/doc/doc2.tex
fancy graphs

Social networks such as Facebook are becoming increasingly important for online news services: an increasing number of their readers access the news pages via links in the networks. Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends. This has led to the development of social media into an important generator of traffic on the internet pages. In Germany, 94\% of online news articles are shared on Facebook in 2015, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}. The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues. For this reason, news agencies are particularly interested in finding out which topics are often shared on Facebook. \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic. FOCUS Online is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.

@@

Within topic models the Latent Dirichlet Allocation (LDA henceforth) is a widely used topic modeling technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution). To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used. LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process \citep{blei_latent_2003}. Thus, it is not ideally suited to examining differences in topical content that are affected by covariates such as author identity or time of writing.

\citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence. We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to vary across newswire services. We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the number of Facebook shares.

>>>>

Social networks such as Facebook are becoming more and more important for online news services: an increasing number of their readers access the news pages via links in the networks. Users of Facebook, for example, can use their profile to share links to external websites - such as news portals - with their online friends. This has led to the development of social media into an important generator of traffic on the internet pages. In Germany, 94\% of online shared news articles in 2015 are distributed via Facebook, followed by Twitter with 3.5\% and Google+ with 2.3\% \citep{schiller_development_2016}. The advertising-financed business model of the media houses is based on the premise that users visit their websites in order to achieve high advertising revenues. For this reason, news agencies are particularly interested in finding out which topics are more likely shared on these platforms. \citet{schiller_development_2016} show, that social media users choose a certain site depending on the researched topic. FOCUS Online for example is targeted for articles from politics and business, sports news is more likely to be shared from Bild.de.

@@

Within topic models the Latent Dirichlet Allocation (LDA henceforth) is a widely used topic modeling technique, where each document (article) is viewed as a mixture of topics (represented by the document-topic distribution) and each topic is a mixture of unique terms (represented by the topic-term distribution). To "learn" the topic prevalence and the topic-term distribution, collapsed Gibbs sampling\footnote{See Section \ref{section_gibbs} for a non-formal description of the Gibbs sampler} can be used.

LDA makes a statistical assumption that all texts in the modeled corpus are generated by the same underlying process \citep{blei_latent_2003}. Thus, it is not ideally suited to examining differences in topical content that are affected by covariates such as author identity or time of writing. \citet{roberts_model_2016} develop a structural topic model (STM) that allows to incorporate external variables that effect both topical content and topical prevalence. We use this approach to analyze online news about the german federal elections, where we allow prevalence of topics to vary across newswire services. We then estimate the effect of topical prevalence (the posterior document-topic distribution) on the number of Facebook shares.
